---
title: "Classifying Motifs to Chromatin Loops with annotator3D"
output: 
  rmarkdown::html_vignette
  toc: true
vignette: >
  %\VignetteIndexEntry{ClassifyingMotifstoChromatinLoops}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

# Introduction

The package **annotator3D** `r packageVersion("mclust")` is an R package to classify DNA motifs or features into chromatin loops. There are four public or private functions in **annotator3D**:
* **Public functions**:
    *`classify` which acts as a master function to classify the motifs/features; and
    * `visualize_annotation` which returns an **ggbio** annotation track.
* **Private functions**:
    * `bin_motifs`, a helper function to `classify`. It calculates the frequencies of the feature in different loops.
    *`calculate_overflow`, a helper function to `bin_motifs`. It calculates how much of a feature overlaps with the loop region.

To give you an idea of how to use the functions, follow along with this tutorial.

# Loading annotator3D
```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(annotator3D)
sessionInfo()
```

# Loading Sample Data
First let's load the chromatin loops dataset from
```{r load_data}
data("mESC_matrix_interactions")
head(mESC_matrix_interactions)
```
Now to load a mapped feature

# Classifying Motifs into Chromatin Loops

# Visualize Classified Motifs
1. histogram of mappings

1. select most significant mapping
2. get positions of mappings -> parse into ranges
3. return annotation track
